Exploring Alternative Routes Using Multipath TCP

### 2017-05-30 paper/presentation.tex
presentation: related work

\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}
\usepackage{wrapfig}
\usepackage[export]{adjustbox}
\usepackage{graphicx}
\usepackage{fancyvrb}
\setbeamertemplate{note page}[plain]
\setbeameroption{show notes on second screen=right}
\setbeamertemplate{navigation symbols}{}%remove navigation symbols

@@

\newcommand{\SectionHead}[2]{
  \begin{frame}{#1}
    \tableofcontents[currentsection,hideallsubsections]
    \note{#1}
  \end{frame}
}

@@

\section{Related Work}
\section{Implementation}
\section{Evaluation}
\section{Conclusion}

>>>>

\usepackage{appendixnumberbeamer}
\usepackage{pgfpages}
\usepackage{wrapfig}
\usepackage[export]{adjustbox}
\usepackage{graphicx}
\usepackage{fancyvrb}
\setbeamertemplate{note page}[plain]
\setbeameroption{show notes on second screen=right}
\setbeamertemplate{navigation symbols}{}%remove navigation symbols
\AtBeginNote{%
    \let\enumerate\itemize%
    \let\endenumerate\enditemize%
}

@@

\newcommand{\SectionHead}[2]{
  \begin{frame}{#1}
    \tableofcontents[currentsection,hideallsubsections]
    \note{#2}
  \end{frame}
}

@@

\section{Related Work}
\SectionHead{}{
  Would love to discuss more, but limited time
}

\subsection{Overlay Networks}

\begin{frame}
  \frametitle{Resilient Overlay Networks}

  \begin{itemize}
  \item Rather than use only one detour, create an overlay network
  \item Overlay nodes use the Internet as their ``link layer''
    \note[item]{In Intro, discussed Detour study. RON is something of a
      spiritual successor. Rather than simple detours, use overlay networks.}
  \item Routing performed at each node using measured link characteristics
    \note[item]{Each node is an Internet host. Constantly monitoring link
      characteristics of network, updating routing tables with performance
      metrics.}
  \item Several studies based on RON:
    \note[item]{RON achieved good results, was testbed for additional studies.}
    \begin{itemize}
    \item Redundant multipath routing
      \note[item]{One study compared two routing strategies: adaptively choosing
      the best path, or redundantly using multiple paths. No aggregation.}
  \item ``Biologically inspired'' multipath routing
    \note[item]{Another - biologically inspired. Choose strongest path as
      primary, have several backups, involves differential equations and
      randomness.}
  \item mTCP \note[item]{mTCP: most important. A modification of TCP before
      MPTCP existed. Built on RON + userspace TCP stack. Did not have MPTCP
      compatibility concerns - routed segments across different paths. Worked on
      single-homed devices due to RON}
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Other Related Items}

  \note[item]{Outside of overlay networks, several related pieces of work, both
    in research and in the standards bodies.}

  \begin{itemize}
  \item Source routing (IPv4) and segment routing (IPv6)
    \note[item]{Notable - it is possible to specify intermediaries in both IPv4
      and IPv6. For security reasons these aren't respected. Standards exist
      mainly for use in internal networks.}
  \item Binder: aggregating bandwidth of several Internet gateways
    \note[item]{One use of MPTCP that is very similar was called Binder. A rural
      town was away from any ISP. Had several potential gateways far away, but
      low bandwidth and not good reliability. Established connections across
      each gateway, and created an OpenVPN connection to an Internet-side
      server, with subflow across each.}
  \item SOSR: Scalable One-hop Source Routing \note[item]{Work inspired by RON,
      but trying to simplify. This work simply tunneled connections across a
      single hop, using a NAT approach similar to ours. Found they got most of
      RON's benefit without the full overlay system.}
  \item IETF MPTCP proxying draft
    \note[item]{Similar because allows single-homed devices to use MPTCP.
      However this approach expects non MPTCP server, and is ``transparent''
      proxy.}
  \end{itemize}
\end{frame}

\section{Implementation}
\section{Evaluation}
\section{Conclusion}
